\documentclass{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}


\title{Ground control}

\begin{document}

\maketitle
\section{Sources of variability in the ground control}
\subsection{Geographical splitting}
First, we have to know that the ground control in \textit{Roissy-CDG} is split between two control towers: one for the north part and another one for the south part. 

Some tasks are different between the north and and south. For example, GCs on the north part have to handle with push-backs when there are some specific apron controllers who do that for the south part of the field (in fact from 10pm to 7am, there is no apron controller and the GCs have to handle it also on the south). For each part, there is a ground controller who can choose to split his part in two more sections each of which is covered by one specific radio frequency. If the ground controller works on the full part, he or she merges the two radio frequencies. So once the GC asks for a splitting, there is also a splitting of radio frequency. The only people who can ask for a splitting is the GC. It happens often too late and the handover becomes difficult. 

We have to understand that the more planes the GC has to handle, the less effective his or her work is, but also that when they choose to split the area, the communication between them becomes essential and are not so easy given that they have to give instructions to planes they are in charge of, listen to them, think about their strategies, and speak to other controllers. Moreover, between two section, planes have to stop to ensure the security. So the splitting of the work is an decision which has some important effects on the taxitime. 

\subsection{Next shift}
Another event that can cause a lengthening of the taxitime is the arrival of a new shift. The current GC has to give information about the traffic, the weather, the tools' condition and in the same time continue following the planes. Moreover according to the time available for the current and the new GC, the change can be quite brutal and in high workload situation, it can difficult to handle. 
\subsection{Ground controllers' tools}
GCs work with only few tools:
\begin{itemize}
    \item Their eyes to see the planes, the traffic and to have a global picture of what happen in their section;
    \item The radio to speak with pilots. GCs have also a phone in order to call agents in other rooms or GCs in the same rooms if the direct communication is not possible. 
    \item A radar screen (named AVISO) to follow planes. It also provides information about speed, type of plane, assigned runway ...
    \item Paper strips. Each plane is represented by a strip of paper on which the GC writes orders he gives to the plane. 10-15 minutes before it would be needed, GCs receive the strip attached to a plane. 
\end{itemize}
\subsection{Communication}
\subsubsection*{With ground controllers}
In order to coordinate the work of ground controllers, they use to exchange a lot of information. They can do it directly or by using their phones if it is easier. They are exchanging information about current planes, potential sources of traffic's complexity or incoming strategy.
\subsubsection*{With other controllers}
GCs use to communicate with other controllers about all non-standard events. They use their phones if the controllers are not in the same rooms.
\subsubsection*{With pilots}
The first rule in the taxiing is that pilots can not do something without the clearance gived by the GC. They are talking together by radio, using the frequency that covers this geographical part of the field. The more complex the traffic is, the less visibility the GC has. The GC can give a total or partial clearance to pilots. Between each section pilots have to change the frequency they are using and to wait to be in touch with the new GC who is handling them to carry on their taxiing. 

\end{document}
