\documentclass{article}

\begin{document}
		\title{Considerations}
	\maketitle
	
In light of the recent interview with the ground controllers, I re-evaluated the goal of the project. In fact, the range of action and of decision of the ground controllers is really restricted, since the main decisions of what runway to assign to each flight, and what time does the aircraft has to leave the stand are taken thanks to a decision-support tool, the departure manager, while the taxiways used are the standard ones, if there isn't any inconvenient.

How is it possible then to reduce the taxi time?
In literature there are two main ways to do so: 
\begin{enumerate}
	\item Finding a best path different from the standard one. In fact, in case of conflicts it could be necessary to quickly compute a new path for every aircraft in the platform, that could avoid the delay.
	\item Re-schedule the TOBT in an optimized way. In fact, as it is calculated now it doesn't take into account eventual inconvenient, such as an aircraft stuck in the taxiway or the need to stop during taxiing because of conflicts with other aircraft.
\end{enumerate}

Those two approaches have three main consequences:

\begin{enumerate}
	\item The Agent Based Model wouldn't be the best way to simulate the system, since we try to compute and deal with pre-determined paths and not with agents that choose a strategy.
	\item The optimized path/schedule would be available to ground controllers only integrating the software in the decision making process.
\end{enumerate}

There is a third unexplored way 

\end{document}
