\documentclass{article}

\begin{document}
		
	\title{Ground controllers interview}
	\maketitle
Here is a set of questions to ask to ground controllers:

\begin{itemize}
    \item Personal information:
        \begin{enumerate}
            \item Age, gender, educational background.
            \item For how many years are you working at Roissy-CDG? Did you work on other airports? Is there any distinctive feature at Roissy-CDG? 
            \item Could you describe your working rhythm?
		\end{enumerate}
    \item Ground controller's practices:
    		\begin{enumerate}
            \item Is your workload constant? 
            \item What are the situations of high workload for you? For each of them, describe your strategy.
            \item What are your strategies during situations of low workload?
            \item What's the maximum number of aircraft you have to handle at the time?
            \item How do pilots take part in decisions? Do your decisions change according to pilots?
            \item From the data, it emerges that only for 55\% of departing flights to a same destination it is assigned the same runway more than 80\% of the time. For the other destinations, the runway is assigned following criteria that are different from the direction of the destination. What is the strategy of runway assignment, in case it doesn't depend on the direction of the destination?
            \item Why in your opinion isn't the ground controller job completely automated? How autonomous do you think you are?
            \item Could you describe your working schedule? Do you usually work during day time or night time? For how long?
            
        \end{enumerate}
    \item Ground controller's practices:
        \begin{enumerate}
        	\item Could you briefly describe the main tasks of your job?
        	\item Do you think you can distinguish between phases of high workload and low workload in your job? 
        	\item If yes, what are the situation of high workload and those of low workload? For each of those situation, describe your strategy.
            \item What's the maximum number of aircraft you have to handle at the same time?
            \item From the data, it emerges that only for 55\% of departing flights to a same destination it is assigned the same runway more than 80\% of the time. For the other destinations, the runway is assigned following criteria that are different from the direction of the destination. What is the strategy of runway assignment, in case it doesn't depend on the direction of the destination?
            \item The ground controller job can't be replaced by automation. What do you think it is the added value of your work that a machine couldn't accomplish?
        \end{enumerate}
    \item Communication:
        \begin{enumerate}
            \item What are the supervisor tasks? How and which kind of information do you exchange with him during your work?
            \item What are the delivery controller tasks? How and which kind of information do you exchange with him during your work?
            \item What are the runway controller tasks? How and which kind of information do you exchange with him during your work?
            \item What are the apron agent tasks? How and which kind of information do you exchange with him during your work?
            \item What are the airport operators with which you exchange information (for example, de-icing companies..)? How and which kind of information do you exchange with them during your work?
            \item Apart from the pilots, can you think of other figures with which you exchange information? Or from which you receive information (EUROCONTROL, aicraft operators...)?
            How and which kind of information do you exchange with them during your work?
        
            \item What are the supervisor tasks? Do you exchange information with him during your work?
            \item How and how often does the communication with pilots take place during taxiing? What information do you exchange? What difficulties do you encounter during the communication with pilots? 
            \item How and how often does the communication with pilots take place during taxiing? What information do you exchange? 
            \item What difficulties do you encounter during the communication with pilots? Can there be any misunderstandings?
            \item Do you communicate differently with a pilot that you know with respect to one that you don't know?
            \item How and how often does the communication with apron controllers take place? What information do you exchange?
            \item Do you communicate with the three other ground controllers during rush hours? What kind of information do you exchange?
        \end{enumerate}
        
    \item Available information:
        \begin{enumerate}
            \item Do you get the position of aircraft by seeing them or by radar detection?
            \item How long in advance can you foresee that you will have a conflict between two or more aircraft on the taxiway? How do you realize it? What do you do when it happens?
            \item What are your tasks and what are those of the DMAN? 
            \item Do you always follow suggestions of the DMAN? If not, why?
            \item Do you always follow suggestions of the DMAN? If not, why? Is it because you don't trust it?
            \item At which percentage of your activity would you estimate the time you take you own decision (compared to the algorithm)? 
        \end{enumerate}
    \item Open question:
    \begin{enumerate}

        \item Could you tell us the most tragic working experience you had?

        \item Could you tell us the most stressful working experience you had?
    \end{enumerate}
	
	\end{itemize}
\end{document}
